---
title: "p8105_hw5_lvr2115"
author: "Laura Robles-Torres"
date: "2023-11-13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(rvest)
library(purrr)
```

 
# Problem 2

## Import and tidy data

```{r import and tidy, echo=TRUE, message=FALSE, warning=FALSE}

raw_data = 
  tibble(
    files = list.files("./data"),
    path = str_c("./data/", files)
  ) |>
  mutate(data = map(path, read_csv)) |>
  unnest(data) 

tidy_data =
  raw_data |> 
   janitor::clean_names() |> 
   separate(files, sep="_", into = c("study_arm", "subject_id")) |>
   separate(subject_id, sep=".csv", into=c("subject_id")) |>
   mutate(study_arm = recode(study_arm, "con" = "Control", "exp" = "Experiment")) |>
   pivot_longer(
    cols = starts_with("week"),
    names_prefix = "week_",
    names_to = "week_num",
    values_to = "obs"
  ) |>
  mutate(
     week_num = as.numeric(week_num)) |>
  select(study_arm, subject_id, week_num, obs)
```

This spaghetti plot shows observations on each subject in the control and the experimental group over time. This plot shows that the experimental group's observed values increased as the study progressed from week 1 to week 8, showing a positive association between observed value and time. The control group's observed values range do not show this trend. The control group's observed values on week 8 are all lower than the experimental group's observed values on the same week. 

```{r plot}
ggplot(tidy_data, aes(x = week_num, y = obs , color = subject_id)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ study_arm) +
  labs(
    x = "Week", 
    y = "Observed value",
    title = "Changes in observed value per study arm over time",
    color = "Subject ID"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Problem 3

### T-test function
```{r function define, echo =TRUE}
# T-test function
sim_ttest = function(n=30, mu=0, sigma=5) {
  
  ttest_data = tibble(
    x=rnorm(n,mean=mu,sd=sigma),
  )

  ttest_data |>
    t.test(alpha=0.05) |>
    broom::tidy() |>
    select(estimate, p.value)
}
```

### Generating 5000 samples with mean = 0 

```{r generate samples, echo=TRUE}
output = vector("list", 5000) 
#output: a list of 5000 values

for (i in 1:5000) {
  output[[i]] = sim_ttest(mu=0) 
#for loop
}

sim_result = bind_rows(output)
```

### Iteration: mu {1 thru 6}

```{r iteration, echo=TRUE}
sim_results=
  expand_grid(
    mean_size = 1:6,
    iteration = 1:5000) |>
  mutate(
    result = map(mean_size, ~sim_ttest(mu = .x))) |>
  unnest(result)

dim(sim_results)
head(sim_results)

```

This plot shows the proportion of times the null was rejected (the power of the test) on the y-axis and the true value of μ on the x axis.

We can see that the proportion of rejected increases as true mean increases. Therefore, power is increasing as effect size increases and flattens out as it approaches 1.

```{r power and mu plot}
sim_results |>
  group_by(mean_size) |>
  filter(p.value < 0.05) |> 
  summarize(rejected_n = n()) |> 
  mutate(
    rejected_n = rejected_n / 5000
  ) |> 
  ggplot(aes(x = mean_size,y = rejected_n)) +
  geom_point() + geom_line() +
  labs(
    x = "True mean",
    y = "Power",
    title = "Relationship of power as true mean increases")
```

This plot shows the average estimate of μ on the y-axis and the true value of μ on the x-axis.

```{r avg estimate and true mu plot}
sim_results |>
  group_by(mean_size) |> 
  summarize(avg_estimate = mean(estimate)) |>
  ggplot(aes(x = mean_size,y = avg_estimate)) +
  geom_point()+ geom_line() +
  labs(x = "True μ",y = "Average Estimate Mean",title = "Estimated Means")
```

This plot shows the average estimate of μ *only in samples for which the null was rejected* on the y-axis
and the true value of μ on the x-axis. 

```{r avg estimate and tru mu only rejected plot}
sim_results |>
  filter(p.value < 0.05) |> 
  group_by(mean_size) |> 
  summarize(avg_estimate = mean(estimate)) |>
  ggplot(aes(x = mean_size,y = avg_estimate)) +
  geom_point()+ geom_line() +
  labs(x = "True μ",y = "Average Estimate of μ",title = "Avg estimate of μ compared to true μ when p< 0.05")
```

The sample average of mu across tests for which the null is rejected is approximately equal to the true value of mu when true mu equals 4, 5 and 6. However, when mu equals 1,2,3 , sample average and true mu are visibly not equal. 